A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 10_applications.tex
make toolpaths plural when separate extrusion paths are considered

Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}). 
These structures are accurately densely filled using our framework.
Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.

>>>>

Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}). 
These structures are accurately densely filled using our framework.
Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
\Cref{applications_hex} shows the contour-parallel toolpath\revise{}{s} with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath\revise{}{s} would create for such a case~\cite{bates2018compressive}.

### 2020-01-29 1_intro.tex
make toolpaths plural when separate extrusion paths are considered

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

>>>>

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath\revise{}{s} using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath\revise{}{s} with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

### 2020-01-29 2_related_work.tex
make toolpaths plural when separate extrusion paths are considered

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
%Toolpath generation for deposition based additive manufacturing consists in generating geometric paths which the nozzle follow during printing.
%Extrusion toolpaths are generated within the planar contour of a layer at the intersection of a horizontal plane and a 3D solid object.
Toolpath generation consists in generating a path in the a planar contour, representing the intersection of a plane and a 3D solid object.
The nozzle is then instructed to move along the path while extruding material.
Sites along the toolpath are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on \revise{generating toolpath that seamlessly fills the entire 2D contour.}{the generation of toolpaths for dense regions, such as the boundary shell of 3D shapes.}
This is sometimes called `dense infill'~\cite{Livesu2017CGF}.

@@

% basic toolpath strategies and their variations
Two basic strategies for dense toolpath generation are \revise{}{the }direction-parallel\revise{}{ strategy} and \revise{}{the }contour-parallel\revise{}{ strategy}.
Direction-parallel (or zig-zag) toolpaths fill an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked together at one of their extremities, to avoid discontinuous extrusion.
Contour-parallel toolpaths typically consists of a set of equally spaced offsets from the slice boundary outline polygons.
\citeauthor{steuben2016implicit} presented a method for generating sparse infill toolpaths based on the isocontours of surface plots of some variable generated on each 2D contour~\cite{steuben2016implicit}.
In order to increase the continuity of contour-parallel toolpaths, a strategy to connect dense toolpaths into spirals was introduced by \citeauthor{Zhao2016}~\cite{Zhao2016} and later extended to also connect a mixture of dense and sparse toolpaths together~\cite{KUIPERS2019CAD}.
\citeauthor{Jin2017RCIM} discusses several approaches for connecting direction-parallel and contour-parallel toolpaths into continuous paths~\cite{Jin2017RCIM}.
Spiral toolpaths have also been applied to (CNC) machining~\cite{Held2009,Huang2017}.
One of the problems with contour-parallel toolpath is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
This is due to the fact that the diameter of the part is not exact multiple of the (constant) deposition width in those regions.
To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are several contour-parallel curves, while \revise{in }{}the interior is filled using a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Reducing under- and over-filling can be accurately achieved by making use \revise{over}{of} adaptive \revise{depisition}{deposition} width.
Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
Their approach handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
However, this extension inherits a problem in the original method:
from any point in the skeleton to the boundary, the number of toolpaths is constant.
\revise{%sdg
Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
}{%f
Depending on the size of small and large features in the layer outlines, this strategy can require a range of bead widths beyond the capabilities of the manufacturing system.
}%sagd
\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting \revise{variation of width in the center is still up to a factor of $2$}{beads have widths within the wide range of $[0.25w,1.8w]$} (see \cref{intro_wedge_centered}).
In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme \revise{deviations}{variation} in width (see \cref{intro_wedge_distributed}).

>>>>

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
%Toolpath generation for deposition based additive manufacturing consists in generating geometric paths which the nozzle follow during printing.
%Extrusion toolpaths are generated within the planar contour of a layer at the intersection of a horizontal plane and a 3D solid object.
Toolpath generation consists in generating a path in the a planar contour, representing the intersection of a plane and a 3D solid object.
The nozzle is then instructed to move along the path while extruding material.
Sites along the toolpath\revise{}{s} are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on \revise{generating toolpath that seamlessly fills the entire 2D contour.}{the generation of toolpaths for dense regions, such as the boundary shell of 3D shapes.}
This is sometimes called `dense infill'~\cite{Livesu2017CGF}.

@@

% basic toolpath strategies and their variations
Two basic strategies for dense toolpath generation are \revise{}{the }direction-parallel\revise{}{ strategy} and \revise{}{the }contour-parallel\revise{}{ strategy}.
Direction-parallel (or zig-zag) toolpaths fill an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked together at one of their extremities, to avoid discontinuous extrusion.
Contour-parallel toolpaths typically consists of a set of equally spaced offsets from the slice boundary outline polygons.
\citeauthor{steuben2016implicit} presented a method for generating sparse infill toolpaths based on the isocontours of surface plots of some variable generated on each 2D contour~\cite{steuben2016implicit}.
In order to increase the continuity of contour-parallel toolpaths, a strategy to connect dense toolpaths into spirals was introduced by \citeauthor{Zhao2016}~\cite{Zhao2016} and later extended to also connect a mixture of dense and sparse toolpaths together~\cite{KUIPERS2019CAD}.
\citeauthor{Jin2017RCIM} discusses several approaches for connecting direction-parallel and contour-parallel toolpaths into continuous paths~\cite{Jin2017RCIM}.
Spiral toolpaths have also been applied to (CNC) machining~\cite{Held2009,Huang2017}.
One of the problems with contour-parallel toolpath\revise{}{s} is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
This is due to the fact that the diameter of the part is not exact multiple of the (constant) deposition width in those regions.
To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are several contour-parallel curves, while \revise{in }{}the interior is filled using a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Reducing under- and over-filling can be accurately achieved by making use \revise{over}{of} adaptive \revise{depisition}{deposition} width.
Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
Their approach handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
However, this extension inherits a problem in the original method:
from any point in the skeleton to the boundary, the number of toolpaths is constant.
\revise{%sdg
Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
}{%f
Depending on the size of small and large features in the layer outlines, this strategy can require a range of bead widths beyond the capabilities of the manufacturing system.
}%sagd
\citeauthor{Jin2017JMS} proposed a strategy of adding \revise{a }{}toolpath\revise{}{s} with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting \revise{variation of width in the center is still up to a factor of $2$}{beads have widths within the wide range of $[0.25w,1.8w]$} (see \cref{intro_wedge_centered}).
In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme \revise{deviations}{variation} in width (see \cref{intro_wedge_distributed}).

### 2020-01-29 4_method.tex
make toolpaths plural when separate extrusion paths are considered

Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
Our skeleton is} based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).

>>>>

Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
Our skeleton is} based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
Contour-parallel toolpath\revise{}{s} with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).
